Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Update discussion of cosmo sims

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F,
2022ApJ...940...61F}. However, the pattern speeds of bars in both cosmological
simulations and the real universe can be affected by environmental processes not
included in our simulation -- e.g., satellite infall
\citep{2011Natur.477..301P}, non-sphericity \citep{2013MNRAS.429.1949A},
rotation in the dark matter halo \citep{2013MNRAS.434.1287S,
2014ApJ...783L..18L, 2018MNRAS.476.1331C, 2019MNRAS.488.5788C}, or perhaps even
the gaseous circumgalactic medium. Naturally, extending our present work to
account for such effects is a crucial next step in understanding the formation
and evolution of galactic bars. We are presently engaged in such an exploration.
We note that \citet{2022ApJ...940...61F} argue that bars in the TNG50 simulation
are too short rather than too slow.

>>>>

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F,
2022ApJ...940...61F}.\footnote{Though see \citet{2022ApJ...940...61F} who argue
bars have consistent pattern speeds with observations, but are too short.}
\citet{2015PASJ...67...63O} describe cosmological zoom simulations of two barred
Milky Way-like galaxies that both slow down over time. As pointed out by
\citet{2010ApJ...719.1470V}, the gas fraction cutoff for the stable pattern
speed regime increases with lower softening lengths. \citet{2015PASJ...67...63O}
use softening lengths larger than ours by about a factor of $6$. This highlights
the importance of future work exploring precisely when barred galaxies ought to
be in the stable regime.

Furthermore, the pattern speeds of bars in both cosmological simulations and the
real universe can be affected by environmental processes not included in our
simulation -- e.g., satellite infall \citep{2011Natur.477..301P}, non-sphericity
\citep{2013MNRAS.429.1949A}, rotation in the dark matter halo
\citep{2013MNRAS.434.1287S, 2014ApJ...783L..18L, 2018MNRAS.476.1331C,
2019MNRAS.488.5788C}, or perhaps even the gaseous circumgalactic medium.
Naturally, extending our present work to account for such effects is a crucial
next step in understanding the formation and evolution of galactic bars. We are
presently engaged in such an exploration.
